Transfer report

### 2019-02-08 Report/final-results.Rmd
Updates pointing chart

ggplot(point_data_1, aes(x = graph.learning.condition, y = abs_error, fill = graph.learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error in degrees after learning phase") + xlab("Learning condition") + 
  scale_fill_manual(values = estimote_pal, "Learning condition")  + guides(fill=F)

>>>>

ggplot(point_data_1, aes(x = graph.learning.condition, y = abs_error, fill = graph.learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average pointing error after learning phase") + xlab("Learning condition") + 
  scale_fill_manual(values = estimote_pal, "Learning condition") +
  guides(fill=F) + theme(axis.title.y = element_text(size = rel(0.9)))
